\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\section*{One-Way ANOVA: Wind Speed and Transpiration}

A study was conducted to assess the effect of wind speed on transpiration in plants. The study involved 15 string bean plants exposed to different wind speeds: low, high, and no wind. The decrease in water in each cylinder was recorded, and the results are analyzed using one-way ANOVA.

\subsection*{ANOVA Table Setup}

Given data:

\[
\text{Group Sum of Squares (SS)} = 53.43
\]
\[
\text{Residual Sum of Squares (SS)} = 12.50
\]

To complete the ANOVA table:

1. **Degrees of Freedom**

   \[
   \text{DF}_{\text{WindSpeed}} = k - 1 = 3 - 1 = 2
   \]
   \[
   \text{DF}_{\text{Residuals}} = N - k = 15 - 3 = 12
   \]
   \[
   \text{DF}_{\text{Total}} = N - 1 = 15 - 1 = 14
   \]

2. **Mean Sum of Squares**

   \[
   \text{MS}_{\text{WindSpeed}} = \frac{\text{SS}_{\text{WindSpeed}}}{\text{DF}_{\text{WindSpeed}}} = \frac{53.43}{2} = 26.715
   \]
   \[
   \text{MS}_{\text{Residuals}} = \frac{\text{SS}_{\text{Residuals}}}{\text{DF}_{\text{Residuals}}} = \frac{12.50}{12} \approx 1.042
   \]

3. **F-Statistic**

   \[
   F = \frac{\text{MS}_{\text{WindSpeed}}}{\text{MS}_{\text{Residuals}}} = \frac{26.715}{1.042} \approx 25.65
   \]

   From the ANOVA table, the p-value is \( 4.64 \times 10^{-5} \), indicating very strong evidence of differences in mean water loss between the three wind speeds.

4. **R-Squared**

   \[
   R^2 = \frac{\text{SS}_{\text{WindSpeed}}}{\text{SS}_{\text{Total}}}
   \]

   To find \(\text{SS}_{\text{Total}}\), we add the group and residual sums of squares:

   \[
   \text{SS}_{\text{Total}} = \text{SS}_{\text{WindSpeed}} + \text{SS}_{\text{Residuals}} = 53.43 + 12.50 = 65.93
   \]

   Therefore,

   \[
   R^2 = \frac{53.43}{65.93} \approx 0.811
   \]

   This indicates that wind speed explains about 81\% of the variability in water loss.

\section*{Juicing Oranges}

A student studied whether warming oranges before juicing affects the amount of juice obtained. After microwaving 15 oranges and keeping 15 unheated, the amount of juice was measured. Using a one-way ANOVA, the results are:

\begin{itemize}
    \item **p-value**: To be determined based on the results from R. It could be one of the following:
    \begin{itemize}
        \item No evidence that warming affects the mean amount of juice obtained.
        \item Weak evidence that warming affects the mean amount of juice obtained.
        \item Moderate evidence that warming affects the mean amount of juice obtained.
        \item Strong evidence that warming affects the mean amount of juice obtained.
    \end{itemize}
    \item **R-squared value**: This value will be determined based on the ANOVA results and should be provided to 3 decimal places.
\end{itemize}

\end{document}
